Pilot study APEROL: questionnaire data

### 2021-01-27 paper_1/paper_1_supplement.Rmd
update manuscript

author: 
  - name          : "Mandy Klatt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Egelstraße 2a 04103 Leipzig"
    email         : "mandy.klatt@uni-leipzig.de"
  - name          : "Gregor Kachel"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Leipzig"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

@@

# value sometimes contained text before filtering, we have to convert the numbers to numeric
quest.raw.data <- quest.raw.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# create a basic table (tibble) using tidyverse functions 
scale.quest.table <- quest.raw.data %>% # select data
  group_by(group, scale) %>%
  summarise("M scale" = round(mean(value), 2),
            "min scale" = min(value),
            "max sclae" = max(value),
            "SD scale" = round(sd(value), 2),
            )

>>>>

author: 
  - name          : "Mandy Klatt"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Egelstraße 2a 04103 Leipzig"
    email         : "mandy.klatt@uni-leipzig.de"
  - name          : "Dr. Gregor Kachel"
    affiliation   : "1, 2"
  - name          : "Dr. Christin Lotz"
    affiliation   : "1"
  - name          : "Prof. Dr. Anne Deiglmayr"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Leipzig"
  - id            : "2"
    institution   : "MPI for Evolutionary Anthropology, Leipzig"

authornote: |
  The study was carried out with the permission of Ethics Committee of the University of Leipzig.

abstract: |
  This document is a supplement to the paper.

@@

# create a basic table (tibble) using tidyverse functions 
scale.quest.table <- quest.raw.data %>% # select data
  group_by(group, scale) %>%
  summarise("M scale" = round(mean(value), 2),
            "min scale" = min(value),
            "max sclae" = max(value),
            "SD scale" = round(sd(value), 2))

### 2021-01-27 paper_1/paper_1_supplement.tex
update manuscript

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher},
  pdfauthor={Mandy Klatt1 \& Gregor Kachel1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\title{Through the eyes of the teacher}
\author{Mandy Klatt\textsuperscript{1} \& Gregor Kachel\textsuperscript{1}}
\date{}

@@

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Leipzig}

\abstract{
Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.
}

@@

\begin{verbatim}
## Warning: Problem with `mutate()` input `value`.
## i NAs durch Umwandlung erzeugt
## i Input `value` is `as.numeric(as.character(factor(value)))`.
\end{verbatim}

\begin{verbatim}
## Warning in mask$eval_all_mutate(dots[[i]]): NAs durch Umwandlung erzeugt
\end{verbatim}

@@

\begin{tabular}{llllll}
\toprule
group & \multicolumn{1}{c}{scale} & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae} & \multicolumn{1}{c}{SD scale}\\
\midrule
expert & Aktivierung und Förderung & 2.82 & 1.00 & 4.00 & 1.11\\
expert & Klarheit und Strukturiertheit & 3.46 & 1.00 & 4.00 & 0.89\\
expert & Klassenmanagement & 3.36 & 1.00 & 4.00 & 0.80\\
expert & Lernförderliches Klima und Motivierung & 3.60 & 2.00 & 4.00 & 0.62\\
expert & Manipulationsitem & 3.55 & 2.00 & 4.00 & 0.69\\
expert & Manipulationsitem & 3.60 & 3.00 & 4.00 & 0.52\\
expert & Präsenz/Haltung\_Blick & 3.29 & 1.00 & 4.00 & 0.92\\
expert & Präsenz/Stimme & 2.70 & 1.00 & 4.00 & 1.16\\
expert & Präsenz/Stimme\ \ & 3.57 & 2.00 & 4.00 & 0.63\\
expert & Präsenz/verbale\_nonberbale Intervention & 3.07 & 2.00 & 4.00 & 0.78\\
expert & Redeanteil & 74.20 & 60.00 & 95.00 & 10.53\\
novice & Aktivierung und Förderung & NA & NA & NA & NA\\
novice & Klarheit und Strukturiertheit & 3.21 & 1.00 & 4.00 & 0.87\\
novice & Klassenmanagement & 2.85 & 0.00 & 4.00 & 0.91\\
novice & Lernförderliches Klima und Motivierung & 3.11 & 0.00 & 4.00 & 0.90\\
novice & Manipulationsitem & 2.90 & 2.00 & 4.00 & 0.45\\
novice & Manipulationsitem & 3.20 & 2.00 & 4.00 & 0.75\\
novice & Nachdenkzeit & NA & NA & NA & NA\\
novice & Präsenz/Haltung\_Blick & 2.95 & 0.00 & 4.00 & 0.95\\
novice & Präsenz/Stimme & 3.19 & 0.00 & 4.00 & 1.04\\
novice & Präsenz/Stimme\ \ & 3.07 & 2.00 & 4.00 & 0.69\\
novice & Präsenz/verbale\_nonberbale Intervention & 2.95 & 1.00 & 4.00 & 0.91\\
novice & Redeanteil & 76.93 & 50.00 & 95.00 & 12.97\\
novice & Störung & NA & NA & NA & NA\\
\bottomrule
\end{tabular}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher},
  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\title{Through the eyes of the teacher}
\author{Mandy Klatt\textsuperscript{1}, Dr.~Gregor Kachel\textsuperscript{1, 2}, Dr.~Christin Lotz\textsuperscript{1}, \& Prof.~Dr.~Anne Deiglmayr\textsuperscript{1}}
\date{}

@@

The study was carried out with the permission of Ethics Committee of the University of Leipzig.

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Leipzig\\\textsuperscript{2} MPI for Evolutionary Anthropology, Leipzig}

\abstract{
This document is a supplement to the paper.
}

@@

\begin{verbatim}
## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA

## Warning in mean.default(value): argument is not numeric or logical: returning NA
\end{verbatim}

\begin{verbatim}
## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
## na.rm): NAs durch Umwandlung erzeugt

## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
## na.rm): NAs durch Umwandlung erzeugt

## Warning in var(if (is.vector(x) || is.factor(x)) x else as.double(x), na.rm =
## na.rm): NAs durch Umwandlung erzeugt
\end{verbatim}

@@

\begin{tabular}{llllll}
\toprule
group & \multicolumn{1}{c}{scale} & \multicolumn{1}{c}{M scale} & \multicolumn{1}{c}{min scale} & \multicolumn{1}{c}{max sclae} & \multicolumn{1}{c}{SD scale}\\
\midrule
expert & Aktivierung und Förderung & NA & 1 & 4 & 1.11\\
expert & Klarheit und Strukturiertheit & NA & 1 & 4 & 0.89\\
expert & Klassenmanagement & NA & 1 & 4 & 0.80\\
expert & Lernförderliches Klima und Motivierung & NA & 2 & 4 & 0.62\\
expert & Manipulationsitem & NA & 2 & 4 & 0.69\\
expert & Manipulationsitem & NA & 3 & 4 & 0.52\\
expert & Präsenz/Haltung\_Blick & NA & 1 & 4 & 0.92\\
expert & Präsenz/Stimme & NA & 1 & 4 & 1.16\\
expert & Präsenz/Stimme\ \ & NA & 2 & 4 & 0.63\\
expert & Präsenz/verbale\_nonberbale Intervention & NA & 2 & 4 & 0.78\\
expert & Redeanteil & NA & 60 & 95 & 10.53\\
novice & Aktivierung und Förderung & NA & - & 4 & NA\\
novice & Klarheit und Strukturiertheit & NA & 1 & 4 & 0.87\\
novice & Klassenmanagement & NA & 0 & 4 & 0.91\\
novice & Lernförderliches Klima und Motivierung & NA & 0 & 4 & 0.90\\
novice & Manipulationsitem & NA & 2 & 4 & 0.45\\
novice & Manipulationsitem & NA & 2 & 4 & 0.75\\
novice & Nachdenkzeit & NA & - & 5-10 & NA\\
novice & Präsenz/Haltung\_Blick & NA & 0 & 4 & 0.95\\
novice & Präsenz/Stimme & NA & 0 & 4 & 1.04\\
novice & Präsenz/Stimme\ \ & NA & 2 & 4 & 0.69\\
novice & Präsenz/verbale\_nonberbale Intervention & NA & 1 & 4 & 0.91\\
novice & Redeanteil & NA & 50 & 95 & 12.97\\
novice & Störung & NA & - & Stift auf Papier schreiben & NA\\
\bottomrule
\end{tabular}

### 2021-01-27 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update manuscript

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
# import: never forget to insert "dec="," for replacing values with "," by "."
raw.data<-read.table("./data/short_questionnaire_data_2101211.txt", dec=",", sep="\t", header=T)

@@

# to compare both sessions filter only Identical items
raw.data <- raw.data  %>% filter(str_detect(shortID, 
                                                 paste(c("km_mitbekommen",
                                                         "km_klar",
                                                         "km_ungestört",
                                                         "km_aktiv",
                                                         "lkm_freundlich",
                                                         "lkm_interesse",
                                                         "lkm_kritik",
                                                         "lkm_ausreden",
                                                         "lkm_überlegen",
                                                         "lkm_rückmeldungen",
                                                         "ks_funktion",
                                                         "ks_verständlich",
                                                         "ks_sichtbar",
                                                         "af_beiträge",
                                                         "af_wechselseitig",
                                                         "af_nachdenken",
                                                         "phb_stand",
                                                         "phb_augen",
                                                         "phb_blick",
                                                         "phb_vorsichgeht",
                                                         "phb_raum",
                                                         "phb_gestik",
                                                         "phb_alleangesehen",
                                                         "ps_deutlich",
                                                         "ps_klar",
                                                         "ps_impulse",
                                                         "pi_nonverbal",
                                                         "pi_zubewegen",
                                                         "pi_direkt",
                                                         "redeanteil",
                                                         "m_natürlich",
                                                         "m_fiktiv",
                                                         "m_verhalten"),
                                                    collapse = '|')))

@@

sum(is.na(raw.data$scale == "Aktivierung und Förderung"))

>>>>

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
# import: never forget to insert "dec="," for replacing values with "," by "."
raw.data<-read.table("./data/short_questionnaire_data_2701211.txt", dec=",", sep="\t", header=T)

@@

# to compare both sessions filter only Identical items
raw.data <- raw.data  %>% filter(str_detect(shortID, 
                                                 paste(c("km_mitbekommen",
                                                         "km_klar",
                                                         "km_ungestört",
                                                         "km_aktiv",
                                                         "lkm_freundlich",
                                                         "lkm_interesse",
                                                         "lkm_kritik",
                                                         "lkm_ausreden",
                                                         "lkm_überlegen",
                                                         "lkm_rückmeldungen",
                                                         "ks_funktion",
                                                         "ks_verständlich",
                                                         "ks_sichtbar",
                                                         "af_beiträge",
                                                         "af_wechselseitig",
                                                         "af_nachdenken",
                                                         "phb_stand",
                                                         "phb_augen",
                                                         "phb_blick",
                                                         "phb_vorsichgeht",
                                                         "phb_raum",
                                                         "phb_gestik",
                                                         "phb_alleangesehen",
                                                         "ps_deutlich",
                                                         "ps_klar",
                                                         "ps_impulse",
                                                         "pi_nonverbal",
                                                         "pi_zubewegen",
                                                         "pi_direkt",
                                                         "m_natürlich",
                                                         "m_fiktiv",
                                                         "m_verhalten"),
                                                    collapse = '|')))

@@
